Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-08 paper/paper.tex
Muck around with conclusion a bit

We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
problems, particularly when edge labels are involved.  We believe there is further scope for
tailoring clique algorithms for association graphs, including specialised inference, a bound
function which is aware that it is working on an association graph, and better initial vertex
orderings. Treating the first branch specially may also be beneficial, since the first branch has an
unusually large effect on the search space with association graphs
\cite{DBLP:conf/cocoon/SutersAZSSL05}.

>>>>

Contradicting earlier claims in the literature, we have seen that a modern clique algorithm can
perform competitively for maximum common subgraph problems, particularly when edge labels are
involved. However, the best approaches for these problems is still far behind the state-of-the-art
for subgraph isomorphism, where we can often scale to unlabelled graphs with thousands of vertices.

To start tackling this gap, we believe there is further scope for tailoring clique algorithms for
association graphs, including specialised inference, a bound function which is aware that it is
working on an association graph, and better initial vertex orderings. Treating the first branch
specially may also be beneficial, since the first branch has an unusually large effect on the search
space with association graphs \cite{DBLP:conf/cocoon/SutersAZSSL05}.
